Exploiting First-Class Arrays in Fortran for Accelerator Programming

### 2010-12-15 opencl/papers/intro.tex
cleaning up verbatim mess
if someone doesn't know what FORTRAN stands for, they shouldn't be     reviewing papers.

Fortran (originally named FORTRAN, the FORmula TRANslation
language\footnote{The capitalization convention for referring the
  language was changed in 1990 to \emph{Fortran}}) is the oldest
high-level programming language in continuous use since its
introduction, and was developed to facilitate the translation of math
formulae into machine code. Fortran was the first major language to
use a compiler to translate from a high-level program representation
to assembly language. Due to its age, it carries certain arcane
baggage that later programming languages have evolved away from. As a
result, Fortran has fallen into disfavor in certain programming
circles.  Modern versions of the language standardized in 1990, 1995, 2003, and 2008
have removed much of this legacy baggage, but these changes are not
widely known.  Modern Fortran exhibits features that are similar to 
other modern programming languages, and does not mandate legacy features
from decades old, deprecated versions of the language.

@@

\begin{verbatim}
do i = 2,(n-1)
  X(i) = (X(i-1) + X(i) + X(i+1)) / 3
end do
\end{verbatim}

@@

\begin{verbatim}
X = (cshift(X,-1) + X + cshift(X,1)) / 3
\end{verbatim}

>>>>

Fortran 
%(originally named FORTRAN, the FORmula TRANslation
%language\footnote{The capitalization convention for referring the
%  language was changed in 1990 to \emph{Fortran}}) 
is the oldest
high-level programming language in continuous use since its
introduction, and was developed to facilitate the translation of math
formulae into machine code. Fortran was the first major language to
use a compiler to translate from a high-level program representation
to assembly language. Due to its age, it carries certain arcane
baggage that later programming languages have evolved away from. As a
result, Fortran has fallen into disfavor in certain programming
circles.  Modern versions of the language standardized in 1990, 1995, 2003, and 2008
have removed much of this legacy baggage, but these changes are not
widely known.  Modern Fortran exhibits features that are similar to 
other modern programming languages, and does not mandate legacy features
from decades old, deprecated versions of the language.

@@

{\small
\begin{verbatim}
do i = 2,(n-1)
  X(i) = (X(i-1) + X(i) + X(i+1)) / 3
end do
\end{verbatim}
}

@@

{\small
\begin{verbatim}
X = (cshift(X,-1) + X + cshift(X,1)) / 3
\end{verbatim}
}
